The impact of forest management on the temperature sensitivity of organic matter turnover

### 2024-10-23 Manuscript_draft/Draft.Rmd
new update of the database and updated figures. Leticia please check I am not making mistakes with the vectors, like wrong labels...

```{r, echo=FALSE}
library(knitr)
anova_results <- read.csv("../Tables/Enzyme_means.csv", stringsAsFactors = FALSE)
kable(anova_results, escape = FALSE, caption = "Table 1: ANOVA Results for enzyme activities")
```

```{r, echo=FALSE}
library(knitr)
anova_results_edaph <- read.csv("../Tables/Edaphics_means.csv", stringsAsFactors = FALSE)
kable(anova_results_edaph, escape = FALSE, caption = "Table 1: ANOVA Results for edaphic and ecological variables")
```

>>>>

```{r, echo=FALSE}
library(knitr)
posteriors <- read.csv("../Tables/posteriors_summary.csv", stringsAsFactors = FALSE)
kable(posteriors, escape = FALSE, caption = "Table 1: posterior probability distributions of the prameters, constant Ea")
```

```{r, echo=FALSE}
library(knitr)
anova_results <- read.csv("../Tables/Enzyme_means.csv", stringsAsFactors = FALSE)
kable(anova_results, escape = FALSE, caption = "Table 2: ANOVA Results for enzyme activities")
```

```{r, echo=FALSE}
library(knitr)
anova_results_edaph <- read.csv("../Tables/Edaphics_means.csv", stringsAsFactors = FALSE)
kable(anova_results_edaph, escape = FALSE, caption = "Table3: ANOVA Results for edaphic and ecological variables")
```
